---
title: "Figure 2 and 3"
author: "Sudarshan A. Shetty"
date: "December 2016"
output: html_document
---

---

```{r, fig.height=6, fig.width=8}
library("reshape")
library("ggplot2")
library("qgraph")

```

###Before we start with the anlaysis there are a few steps that need to be completed.  

1] Download the compelte repository (right hand corner)  
   file that you have downloaded is "Intestinal-Microbiome-Western-Adults-master.zip"
2] Unzip the file "Intestinal-Microbiome-Western-Adults-master.zip" 
3] Set this as the working directory using the command below "setwd()"

```{r cars}
setwd("D:/Intestinal-Microbiome-Western-Adults-master")

# You can check the working directory now by typing
getwd()
```

###We will noe read the files. you have to chose the file ("genome_koabundance.txt") in the new select window that will pop-up after you run the script "file= choose.files(multi=F)"


```{r}
setwd("D:/Intestinal-Microbiome-Western-Adults-master")

file= choose.files(multi=F)
ko_abundance= read.table(file,sep="\t", header=T, row.names=1)

```

## Creating the plots
```{r}
#we now calculate the Spearman rank correlation 
genome.cor<- cor(ko_abundance, method="spearman")

#check the file
head(genome.cor)
#load the following packages
library("reshape")
library("ggplot2")

#format the data for use in ggplot2
cor.dat <- melt(genome.cor)

###Identifying the correlation distribution profile
cor.dist.plot <- ggplot(cor.dat, aes(x=value), geom = "histogram", size= 2, color = "#CC79A7") + stat_bin(binwidth = 0.01, fill = "#807dba") + theme(axis.title.x = element_text(colour = "black", size= 4), axis.title.y = element_text(colour = "black", size=4)) + labs(x= " Correlation values Spearman correlation", y= "Counts" , size= 4) + theme_grey()

print(cor.dist.plot)

```


```{r,fig.height=8, fig.width=8}
#Plot the pairwise Spearman’s correlation
cor.pair.plot <- ggplot(cor.dat, aes(value, X1), geom= "bar", fill= ..count..) + geom_jitter(aes(x=value,y=X1), color = "#807dba", shape=18) + labs(x= " Correlation values (Pearson coefficient)", y= "Genome of representative core bacteria") + scale_x_continuous(limits = c(0.2, 1)) + theme_bw() + theme(axis.text.y = element_text(size=8, face = "italic")) 
print(cor.pair.plot)

```

```{r }
library("qgraph")

#set node attribute
labels_row <- rownames(genome.cor)
set.seed(12134)
qab <- qgraph(genome.cor, minimum = 0.5, fade = TRUE, vsize = 1.5, layout = "spring", vTrans = 255, node.labels= TRUE, edge.labels=FALSE, rotation= "45", labels = labels_row, label.cex = 0.4, label.scale= F, edge.color= "#00CDCD")

```

###Further colouring based on phylum affiliation was done in Adobe.

