---
title: "Intestinal-Microbiome-Western-Adults"
author: "Sudarshan A. Shetty"
output: html_document
---


### R Markdown for the review by Shetty et al. "Intestinal microbiome landscaping: Insight in community assemblage and implications for microbial modulation strategies "

Please use the files available at https://github.com/microsud/Intestinal-Microbiome-Western-Adults

We will make a phyloseq object to easily analyse the data using microbiome package which is maintianed by Leo Lahti (GitHub: https://github.com/antagomir).

The codes and details of these can be found at https://github.com/microbiome/microbiome



```{r }
library(microbiome)
library(phyloseq)
otu_table<- read.csv("D:/../../IGC_genus_data.csv",row.names=1,check.names=FALSE) #we read the otu table first
#abund_table<-t(abund_table)
grouping_info<-data.frame(row.names=rownames(otu_table),t(as.data.frame(strsplit(rownames(otu_table),"_")))) #and check the grouping information
head(grouping_info)
meta_table<-read.csv("D:/../../IGC_Metadata.csv",row.names=1,check.names=T)
sampleData=sample_data(meta_table)
```

Now we merge all the files into one phyloseq object.

```{r }
otumat<-as.matrix(otu_table)
OTU = otu_table(otu_table, taxa_are_rows = TRUE)

sampleData=sample_data(meta_table)
ps.igc <- merge_phyloseq(OTU, sampleData)

##We now need to remove the data from the Chinese population.

igc.eu <-subset_samples(ps.igc, Nationality != "Chinese")
igc.eu <- prune_taxa(taxa_sums(igc.eu) > 0, igc.eu)

```

We set certain threshold to limit the data analysis to only taxa present at a minimum relative abundance of 0.0001 and present in 25% of the samples.
```{r}

igc.eu1 <- filter_prevalent(igc.eu, detection.threshold = 0.0001, prevalence.threshold = 0.25)
head(prevalence(igc.eu1, detection.threshold = 0.0001, sort = TRUE))
head(prevalence(igc.eu1, detection.threshold = 0.0001, sort = TRUE, relative = FALSE))
core.taxa <- core(igc.eu1, detection.threshold = 0.0001, prevalence.threshold = 95)
core.abundance <- core_abundance(igc.eu1, detection.threshold = 0.0001, prevalence.threshold = 95)
core.taxa
```

For plotting the figure we will set certain parameters. 

```{r}

prevalence.intervals <- seq(5, 100, 5)
detection.thresholds <- 10^seq(log10(1e-4), log10(20), length = 20)

library(RColorBrewer)
res <- plot_core(igc.eu1, plot.type = "heatmap",
                 #colours = colorRampPalette(rev(brewer.pal(11, "Spectral")))(5),
                 colours = rev(brewer.pal(5, "Spectral")),
                 prevalence.intervals = prevalence.intervals,
                 detection.thresholds = detection.thresholds,
                 min.prevalence = 50)         
res
library(ggplot2)
res + ggtitle("Phylogenetic Core of 840 Western Adults Based on Metagenomic data") + xlab("Detection Threshold (Relative Abundance %)")

### we will now read check the prevalences and detection thresholds
library(knitr)
prevalences <- res$data
kable(head(prevalences))
kable(prevalences)
prev_k <- kable(prevalences)
prevdf <- as.matrix(prev_k)
write.table(prevdf, "prevalences.txt")

```



